ms_figures

### 2023-02-07 ms_figures.Rmd
updates to diversity and custom artis ts

```{r fig4b}
# NOTE: Rahul - we need to have the correct file read in here. For reference, the file currently generating this and the new fig 4d is "/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv"
# I am not sure we should go with these colors, but didn't have time to keep messing with this
# These comments also apply to the new fig4c

fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

>>>>

```{r fig4b}
# NOTE: Rahul - we need to have the correct file read in here. For reference, the file currently generating this and the new fig 4d is "/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv"
# I am not sure we should go with these colors, but didn't have time to keep messing with this
# These comments also apply to the new fig4c
diversity <- read.csv("/Volumes/jgephart/ARTIS/Outputs/diversity/max_per_capita_100kg/diversity.csv")
fig4b <- diversity %>% 
  filter(year == 2019) %>%
  select(iso3c, region, "Production" = "shannon_prod", "Imports" = "shannon_imports", "Exports" = "shannon_exports") %>% 
  pivot_longer(Production:Exports, names_to = "shannon_var", values_to = "shannon_index") %>%
  mutate(shannon_var = factor(shannon_var, levels = c("Production", "Imports", "Exports"))) %>%
  ggplot(aes(x = shannon_var, y = shannon_index, fill = shannon_var)) +
  geom_violin() + 
  geom_point(alpha = 0.5) +
  scale_fill_manual(values = c(habitat_source_colors[1], habitat_source_colors[3], habitat_source_colors[4])) +
  labs(x = "", y = "Shannon index", fill = "") +
  facet_wrap(~region, nrow=1) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())
